\TheTitle

### 2017-07-12 paper/study.tex
study: Participant profile
I've added information about the participants and their experience with
git.

@@

@@

To mitigate the bias between tools, commits, and tasks, we randomize the
orders.

>>>>

\evan{Do I need to say where the study took place? I see it showing up
  in other papers, but it makes it kind of obvious about the lab I'm
  talking about, doesn't it?}

@@

The study was conducted with 12 participants, all of whom were
masters, PhD, or post-doc researchers in the field of software
engineering. The participants had between 6 months and 10 years
experience with git, with the median being 3.5 years. Most of the
participants had additional experience with SVN and CVS.\@ One of the
participants in the study worked as a release engineer, studying merge
practices to determine the best way to merge branches while minimizing
the number of merge conflicts, on SVN repositories. The participants
worked with repositories ranging from around 10 commits up to 38000
commits, with the median being 350 commits. Two of the participants had
never collaborated with anyone in a repository, while the rest had some
experience with repositories being modified by multiple people, with the
most being 219. The median number of collaborators was four.

Five participants had only worked with personal and academic
repositories. Two participants had only worked with school and
professional repositories, and two had only worked with professional
repositories. One participant worked with personal, academic, and
professional repositories, one participant had only worked with personal
repositories, and one participant had worked with personal, academic,
and school repositories.

\evan{Do you want more information about the participants?}

All participants have had at least some experience with the idea of
version control, branching in repositories, and git. The participants
are all from the same lab, and each participant worked with both tools
in the study, thus, keeping the sample populations identical for both
tools, with some variation between participants in experience with
repositories.

@@

Each task group is applied to both commits, with the order of the commits
randomized between participants to mitigate the effects of order-bias.

The conceptual tasks are the second part of the study. These tasks start
with the participant taking 10 minutes to draw a diagram showing how one
of the commits

% To mitigate the order bias caused by using one tool before the other,
% one commit before the other, and the various tasks, we randomize...
